`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-18 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
minor edits

\section{Discussion}\label{DiscussionSection}
This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. The results indicate good estimation performance, where the mean parameter estimates are in good accordance to the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by a random disturbance and the observations are corrupted by noise. To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings. Following such a paradigm, data can be epoched into a sufficient number of realisations such that a distribution of the estimates can be formed.

@@

The accuracy of the estimation is limited by many factors.

@@

In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual kernel. In future work, we plan to extent this work to relax this assumption. We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions. In addition, we have assumed the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong. Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed. Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite propagation times into the neural field equations.

>>>>

\section{Discussion}\label{DiscussionSection}
This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. The results indicate good estimation performance, where the mean parameter estimates are in good accordance to the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which is expected considering the system is driven by an unknown input, modelled as a random disturbance and the observations are corrupted by noise. To overcome the effect of noise, an evoked-response paradigm should be considered when using electrophysiological recordings. Following such a paradigm, data can be epoched into a sufficient number of realisations such that a distribution of the estimates can be formed.

@@

@@

In this paper, assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption. We hope to achieve this by using the actual kernel that cannot exactly be presented by the chosen finite number of basis functions. In addition, we have assumed the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modelled as being isotropic. However, the assumption of homogeneity is quite strong. Future work should be focussed on developing estimation algorithms where assumption of homogeneity can be relaxed. Future work should also be targeted to include a more realistic synaptic response kernel, with finite rise and decay times and finite, distant dependant propagation times into the parametric neural field equations.
